### 2018-12-10 doc/paper/main.tex
paper/main.tex: Wording and typo

\documentclass[runningheads]{llncs}
	\usepackage[ngerman,english]{babel}  % Language specification
	\usepackage{varioref}  % Better references but possibly unstable
	\usepackage[T1]{fontenc}  % Output umlauts in a PDF
	\usepackage[utf8]{inputenc}
	\usepackage{pslatex}
	\usepackage{amsmath}
	\usepackage{multirow}
	\usepackage{ellipsis}
	\usepackage{textcomp}
	\usepackage{longtable}
	\usepackage{rotating}
	\usepackage[section]{placeins}

	\usepackage[font=small,labelfont=bf]{caption}  % Customize caption aesthetics
	\usepackage[font=small]{subcaption}  % Customize sub-captions

	\usepackage{color}
	\usepackage{xcolor}  % Highlighting
	\usepackage{tcolorbox}  % Fancy colored boxes
	\usepackage{soul}

	\usepackage[tracking=true]{microtype}  % Change character spacing

	\usepackage{graphicx}  % Insert images
	\usepackage{listings}  % Insert programming code
	\usepackage[space]{grffile}  % Insert images baring a filename which contains spaces
	\usepackage{float}  % Forcefully set the location of an object

	\usepackage[style=numeric,sorting=none,backend=biber]{biblatex}  % Reference manager
	\usepackage[bookmarks]{hyperref}  % Clickable references

	\usepackage[nodayofweek]{datetime}  % Flexible date specification
	\usepackage{scrextend}  % Arbitrary indentation

	\addbibresource{../literature.bib}

	% Display URLs in blue roman font if using hyperref to comply with Springer's eBook style
	\renewcommand\UrlFont{\color{blue}\rmfamily}

	\makeatletter
	% Insert a float barrier before subsections just like the package 'placeins' does for sections
	%\AtBeginDocument{%
	%	\expandafter\renewcommand\expandafter\subsection\expandafter{%
	%		\expandafter\@fb@secFB\subsection
	%	}%
	%}
	\makeatother
	\setlength{\intextsep}{1.1em}  % Reduce excessive spacing between float and text
	\setlength{\textfloatsep}{1.1em}  % Reduce excessive spacing between caption and text

	% Use bold sub-caption references
	\DeclareCaptionLabelFormat{bold}{\textbf{#2}}
	\captionsetup{subrefformat=bold}

	%\parindent0em  % Indentation of the first line of a paragraph
	\newcommand{\leadingzero}[1]{\ifnum#1<10 0\the#1\else\the#1\fi}
	\newcommand{\todayddmmyyyy}{\leadingzero{\day}.\leadingzero{\month}.\the\year}
	\newcommand{\mathcolorbox}[2]{\colorbox{#1}{$\displaystyle #2$}}
	\renewcommand{\sectionautorefname}{\ifnum\spacefactor>1000 Section\else section\fi}  % Capitalize 'section' if used after some spacing
	\def\permille{\ensuremath{{}^\text{o}\mkern-5mu/\mkern-3mu_\text{oo}}}  % Permille sign

	\lstset{basicstyle=\ttfamily,breaklines=true}  % Prettier code highlighting style
	\pagestyle{myheadings}  % Prettier page format with header but without footer

\begin{document}

\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}
}
\author{Gordian~Edenhofer\inst{1,2} \and Joeran~Beel\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2}}
\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
\institute{
	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, collinsa@tcd.ie, aizawa@nii.ac.jp}
}

\maketitle  % Typeset the header of the contribution
\markboth{}{}  % Clear the section and author from the page header

\begin{abstract}
The DonorsChoose.org dataset of past donations provides a big and feature-rich corpus of users and items. The dataset matches donors to projects in which they might be interested in and hence is intrinsically about recommendations. Due to the availability of detailed item-, user- and transaction-features, this corpus represents a suitable candidate for meta-learning approaches to be tested. This study aims at providing an augmented corpus for further recommender systems studies to test and evaluate meta-learning approaches. In the augmentation, metadata of collaborative and content-based filtering techniques is amended to the corpus. It is further extended with aggregated statistics for users and transactions and an exemplary meta-learning experiment. The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set. The augmented dataset and the source code are released into the public domain at GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset.

\keywords{recommender systems \and meta-learning \and dataset augmentation \and ensemble learning \and hybrid recommenders.}
\end{abstract}

\section{Introduction}
Meta-Learning is the process of applying machine learning algorithms on metadata as is generated by a subsystem composed of machine learners. The goal of meta-learning systems is to improve existing approaches by combining the strengths of several single machine learning systems. In recommender systems it is an emerging field of interest as meta-learning promises to better sort through item, user and transaction information as to retrieve the best possible match of item and user.

One challenge for researchers interested in meta-learning is that suitable datasets are time-consuming and cumbersome to construct. Creating a system of individual machine learning experiments and amending their metadata to the original corpus takes time and resources away from addressing more important challenges in meta-learning for recommender systems. Multiple examples of manual and repetitious data augmentation may be found in the scientific literature, for instance in~\cite{CUNHA2018128,DBLP:journals/corr/abs-1805-12118,Ekstrand:2012:RFP:2365952.2366002}.

Our objective is to address the data augmentation part in a comprehensive way as to allow researchers to focus on the actual meta-learning evaluation. We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich, vast corpus is a suitable candidate. The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}). It is further amended with aggregated statistics about users and items and metadata of an exemplary experiment.

\section{Methodology}

\subsection{The Dataset}
DonorsChoose.org is an organization which enables teachers to file project requests for resources for their school. Collectively the nonprofit has raised $\$685$ million for classrooms in the United States of America. Their dataset composed of past donations features $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects. The corpus provides significantly more transactions with more detailed item and transaction information compared to, e.g., the popular MovieLens dataset. An exemplary itemized view of the augmented dataset is shown in~\autoref{tab:IllustrativeTable}.

The corpus features comprehensive information on the users~(donors), items~(projects) and transactions respectively interactions~(donations). Transactions are represented by an interaction of a user with an item at a specific point in time and further include a strength~(amount~donated). Users feature information about their location and a boolean value indicating whether they are a teacher. Items feature multiple textual descriptions, funding goals, a list of associated categories and types, information about the creator and details about the location of the school which the item is about.

In a learning subsystem step, two collaborative filtering techniques and two content-based filtering techniques are applied. The performance measures of the single algorithms are amended to the table. Next, aggregated user and item statistics are calculated and added to the table. Lastly, four exemplary meta-learners are applied and the performance measures of the individual approaches are added to the corpus.

\begin{table}[ht]
	\centering
	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}
	\label{tab:IllustrativeTable}
	\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/Illustrative example of the overall design of the augmented transaction table}}}
\end{table}

\subsection{Dataset Preparation}
To prepare the dataset for evaluations, duplicate interactions are merged as the recommender systems shall not recommend items to which the user has already donated to. Internal stop words in description strings of items are stripped. Furthermore, transactions containing no information about the user's location are dropped. Thereby enabling the consistent usage of a user’s location information in new approaches.

Additionally, users having interacted less than twice are removed as well. Although, this limits the target group, the step is unavoidable as the employed validation process requires at least one interaction per user for testing and one for training. The evaluation requires user profiles and hence training-transactions in order to recommend new items which in turn need to be validated against test-transactions. Lastly, the donated amount is transformed to a transaction strength in the range of unity to five in analogy to a rating score. This step reduces the influence of outliers respectively unusual donated amounts.

\subsection{Learning Subsystem}
The learning subsystem is a recommender system itself. SVD and KNN are used as representatives for collaborative filtering techniques and TF-IDF and word-embedding for content-based filters~\cite{scikit-learn,rehurek_lrec}. Hereby, the otherwise intrinsic inductive bias is reduced. The word-embedding relies on fastText and utilizes pre-trained vectors~\cite{DBLP:journals/corr/BojanowskiGJM16}. Vector representations of items are the normalized sum of the vectors of the normalized embeddings of the individual words. In order to work with the data in an efficient way, transactions are sampled. For this study a sample-size of $100,000$ was chosen. This represents a fair balance between required computing time and ability to generalize.

A classical 5-fold cross-validation on the users is applied for training the collaborative filters. Using the recall in a Top-N test set, a score of how good an algorithm is able to recommend an item is calculated. The algorithm is provided with all the items with which the user from the test set has interacted with except for one and is requested to create a ranking of $100$ random items with which the user has not interacted with plus the one with which an interaction has taken place. An ordering is assumed to be implied by the magnitudes of the values in the reconstructed matrix of the decomposition respectively the distance to the neighbor. The position of the interacted item in the set of $101$ items is then used as score for the user-item transaction.

The validation process of the content-based approaches uses leave-one-out. For each transaction a profile of the user is constructed which excludes this transaction. Afterwards, the algorithm is requested to create a ranking of $100$ items with which the user has not interacted with and the one with which a transaction has taken place. The ranking is performed using the cosine similarity of an item’s vector and the user's profile.

The choice of evaluation method ensures that it can be applied to a vast set of different algorithms as long as a ranking of items can be produced and therefore allow for a high variety within the set of algorithms in the learning subsystem. It further ensures that not just the ability to decompose the data is measured but the ability to recommend new items to users~\cite{Cremonesi:2010:PRA:1864708.1864721}. Hereby, the learning subsystem is kept extensible while still providing useful metadata to meta-learning algorithms.

\subsection{Statistics and Application of Learning Subsystem}
The meta-learning system processes the metadata from the learning subsystem and further statistics. Its performance is evaluated via a holdout split on the transaction table using $80\%$ for training and the rest for testing. Transactions are expanded to contain more detailed information about the time, the user's location and aggregated statistics about the mean of the categories, location and interaction-strength of items with which the user has interacted with. Statistics are solely based on the training set. Values for unknown users are filled with the mean in the training data.

Four different meta-learning approaches are discussed which address the Algorithm Selection Problem (ASP) via a switching hybrid ensemble. The aim of the system is to predict the algorithm with the lowest recall-position for each transaction respectively each row in~\autoref{tab:IllustrativeTable}. The overall performance of a meta-learner is measured using the mean recall-position for when the recommended algorithm for each transaction is used.

The first approach aims at predicting the algorithm which will best describe the transaction via a classification based on the given meta-features using a decision tree. The second approach employs a gradient boosting regressor to predict the position of the recall for each transaction and for each algorithm in the learning subsystem separately. As best algorithm, the one with the lowest predicted recall-position is chosen.

The third meta-learner is a classical stacking ensemble using a decision tree which is given the prediction from the learning subsystem as additional input. Based on the metadata and the output of the learning subsystem, it then performs a transaction classification. The final approach aims at solving the ASP via clustering transactions based on the meta-features using K-Means and assigns clusters an overall best algorithm via majority voting.

\section{Results}
The preparation of the dataset preserves a little more than half of the data with the most notable drop in the number of transactions being introduced by requiring users to have donated at least twice. The sample of $100,000$ transactions contains $18,735$ unique users and $88,100$ unique projects.

\begin{figure}[ht]
	\centering
	\subcaptionbox{Interactions Frequency\label{fig:InteractionFrequency}}{
		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/DonorID - Distribution of number of interactions per user}}}
	}
	\hspace{2em}
	\subcaptionbox{Interaction Strength\label{fig:InteractionStrength}}{
		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/DonationAmount - Distribution of ratings for logarithmic bins and excluded outliers}}}
	}
	\caption{The frequency of the number of interactions per user without outliers is shown in~\subref{fig:InteractionFrequency} and the distribution of the transformed interaction strength is shown in~\subref{fig:InteractionStrength}.}\label{fig:Interactions}
\end{figure}

The requirement enforcing users to have interacted at least twice results in a distribution of the number of users interacting with items which decays exponentially as depicted in~\autoref{fig:InteractionFrequency}. This is to be expected as the time users can invest in researching items and their total interaction strength (budget) is limited. The dataset is dominated by users which interacted exactly two times.

The distribution of the transformed interaction strength in analogy to a rating score is shown in~\autoref{fig:InteractionStrength}. It peaks at the second highest score. Interactions with a weak to medium interaction strength and ones with the strongest interaction strength are about equally likely. Interactions with the lowest strength value are very infrequent.

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Learning subsystem - Position in Top-N test set}}}
	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem. The dashed green lines indicate the mean, the straight orange lines the median. The percentage below each algorithm indicates how often it is the best possible algorithm. To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}
	\label{fig:MetaLearnerStatistics}
\end{figure}

Statistical information about the performances are visualized in~\autoref{fig:MetaLearnerStatistics}. It can be observed that the performance of the learning subsystem depends highly on the employed filtering techniques. Overall, content-based filters are significantly better in achieving a low recall-position (average position in Top-N set; content-based filtering:~$19.48$, collaborative filtering:~$83.28$). The algorithm with the poorest performance is KNN. SVD performs better but is still unable to reliably yield good recommendations. Furthermore, grouping users by shared item interactions has no observable positive impact on the recommendation of new items.

Considering the low average number of interactions per user and the vast number of items available, KNN apparently fails to find appropriate neighbors. SVD seems to struggle with the sparsity of the input matrix as looking at the reconstruction of the decomposed matrix it is revealed that most values are well below unity and very similar to each other. SVD yields recall-positions below $10$ infrequently.

Content-based filtering techniques achieve better performance scores on the dataset. User profiles based on TF-IDF and fastText each yield recall-positions below $10$ for roughly half of all transactions with the simpler TF-IDF performing slightly better than fastText. This could be at least in part due to users explicitly searching for specific terms instead of exploring all possible items manually.

Between the different meta-learning approaches, significant changes in the mean recall-position can be noted as seen in~\autoref{fig:MetaLearnerPerformance}. The worst performer is the user-clustering using K-Means (average position in Top-N:~$15.56$). The stacking decision tree performs best (average position in Top-N:~$9.02$). Of the three non-stacking approaches the gradient booster performs best (average position in Top-N:~$11.21$) and achieves a better score than the single best algorithm, i.e., TF-IDF (average position in Top-N:~$11.96$). The classifying decision tree (average position in Top-N:~$15.27$) outperforms the user-clustering but is still notably worse than the overall best algorithm.

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}
	\label{fig:MetaLearnerPerformance}
\end{figure}

That the stacking ensemble performs best is unsurprising as it is provided significantly more information than the other algorithms. The performance of the gradient booster is encouraging as it successfully addresses the ASP. From the poor performance of the user-clustering it can be reasoned that similar transactions do not necessarily yield similar results using the same recommender algorithm. Hence, the similarity of meta-feature does not imply that the performance of recommendations is similar.

The classification and error prediction approach apparently suffer from the level of indirection which is introduced by predicting a single algorithm and disregarding the penalty which is introduced if a bad performing one is chosen. Even a high accuracy in algorithm selection does not guarantee a low mean recall-position. This is partly mitigated by the error prediction approach but still not completely suppressed.

\section{Conclusion}
The study provides an extensively augmented dataset based on the transaction data published by DonorsChoose.org. The corpus is amended with metadata of individual recommender algorithms. Collaborative and content-based filtering techniques are used in the process and their performance is evaluated via the recall in a Top-N test set. Aggregated user and item statistics are amended to the table. Metadata of four switching hybrid ensemble meta-learners is amended to the dataset. The augmented public domain dataset lays the groundwork that future evaluations of existing and novel meta-learning approaches can build upon.

\begin{appendix}
	\printbibliography[heading=bibintoc]
\end{appendix}

\end{document}

### 2018-12-10 doc/compact paper/main.tex
Introduce a compact paper with the same content

--- 2018-12-10 doc/paper/main.tex
@@
-\documentclass[runningheads]{llncs}
+\documentclass{IEEEtran}
+	\usepackage{csquotes}  % For usage with the IEEEtran document class as to avoid warning
 	\usepackage[ngerman,english]{babel}  % Language specification
@@
 	% Display URLs in blue roman font if using hyperref to comply with Springer's eBook style
-	\renewcommand\UrlFont{\color{blue}\rmfamily}
+	%\renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 	\lstset{basicstyle=\ttfamily,breaklines=true}  % Prettier code highlighting style
-	\pagestyle{myheadings}  % Prettier page format with header but without footer
+	%\pagestyle{myheadings}  % Prettier page format with header but without footer
 
@@
 
-\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
-\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
-	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}
-}
-\author{Gordian~Edenhofer\inst{1,2} \and Joeran~Beel\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2}}
-\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
-\institute{
-	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
-	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, collinsa@tcd.ie, aizawa@nii.ac.jp}
+%\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
+\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
+\author{
+	\IEEEauthorblockN{
+		Gordian~Edenhofer\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
+		Joeran~Beel\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}%
+		\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.},
+		Andrew~Collins\IEEEauthorrefmark{1} and
+		Akiko~Aizawa\IEEEauthorrefmark{2}
 	}
 
+	\IEEEauthorblockA{
+		\IEEEauthorrefmark{1}Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland
+	}
+
+	\IEEEauthorblockA{
+		\IEEEauthorrefmark{2}National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan
+	}
+
+	\href{mailto:beelj@tcd.ie}{beelj@tcd.ie},
+	\href{mailto:collinsa@tcd.ie}{collinsa@tcd.ie},
+	\href{mailto:aizawa@nii.ac.jp}{aizawa@nii.ac.jp}
+}
+%\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
+
 \maketitle  % Typeset the header of the contribution
-\markboth{}{}  % Clear the section and author from the page header
+%\markboth{}{}  % Clear the section and author from page headers
 
@@
 The augmented dataset and the source code are released into the public domain at GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset.
+\end{abstract}
 
-\keywords{recommender systems \and meta-learning \and dataset augmentation \and ensemble learning \and hybrid recommenders.}
-\end{abstract}
+\begin{IEEEkeywords}
+	recommender systems, meta-learning, dataset augmentation, ensemble learning, hybrid recommenders.
+\end{IEEEkeywords}
 
@@
 
-\begin{table}[ht]
+\begin{table*}[ht]
 	\centering
@@
 	\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/Illustrative example of the overall design of the augmented transaction table}}}
-\end{table}
+\end{table*}
 
@@
 	\centering
-	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Learning subsystem - Position in Top-N test set}}}
+	\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/Learning subsystem - Position in Top-N test set}}}
 	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem.
@@
 	\centering
-	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
+	\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
 	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}
@@
 
-\begin{appendix}
 \printbibliography[heading=bibintoc]
-\end{appendix}
 

### 2019-02-12 doc/paper/main.tex
paper/main.tex: Incorporate general peer-review
Tweak the introduction to hopefully make it more clear what is being
addressed in this research. Criticize other datasets more and outline
why the RMSE was not chosen. Further, better describe the process of
calculating the mean recall-position in a Top-N set.

Furthermore, drop supervisors except for Andrew, i.e. drop Joeran and
Akiko from the list of authors. Change the repository link to point to
GitHub:Edenhofer instead of GitHub:BeelGroup.

Additionally fix some typos and marginally shrink the space between
figures and text.

@@
 
+	\usepackage[inline]{enumitem}  % Inline enumeration capability
 	\usepackage[font=small,labelfont=bf]{caption}  % Customize caption aesthetics
@@
 	\makeatother
-	\setlength{\intextsep}{1.1em}  % Reduce excessive spacing between float and text
-	\setlength{\textfloatsep}{1.1em}  % Reduce excessive spacing between caption and text
+	\setlength{\intextsep}{1em}  % Reduce excessive spacing between float and text
+	\setlength{\textfloatsep}{1em}  % Reduce excessive spacing between caption and text
 
@@
 \titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
-\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
-	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}
-}
-\author{Gordian~Edenhofer\inst{1,2} \and Joeran~Beel\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2}}
+\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
+\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1}}
 \authorrunning{G. Edenhofer et al.}  % Abbreviated author field
@@
 	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
-	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, collinsa@tcd.ie, aizawa@nii.ac.jp}
+	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{G.Edenhofer@campus.lmu.de, collinsa@tcd.ie}
 }
@@
 The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set.
-The augmented dataset and the source code are released into the public domain at GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset.
+The augmented dataset and the source code are released into the public domain at GitHub:Edenhofer/Augmented-DonorsChoose.org-Dataset.
 
@@
 Meta-Learning is the process of applying machine learning algorithms on metadata as is generated by a subsystem composed of machine learners.
-The goal of meta-learning systems is to improve existing approaches by combining the strengths of several single machine learning systems.
+The goal of meta-learning systems is to improve existing approaches by combining the strengths of several single machine learning systems in an ensemble.
 In recommender systems it is an emerging field of interest as meta-learning promises to better sort through item, user and transaction information as to retrieve the best possible match of item and user.
@@
 One challenge for researchers interested in meta-learning is that suitable datasets are time-consuming and cumbersome to construct.
-Creating a system of individual machine learning experiments and amending their metadata to the original corpus takes time and resources away from addressing more important challenges in meta-learning for recommender systems.
+Creating a system of individual machine learning experiments and amending their metadata to the original corpus takes time and resources away from working with the actual meta-learners.
 Multiple examples of manual and repetitious data augmentation may be found in the scientific literature, for instance in~\cite{CUNHA2018128,DBLP:journals/corr/abs-1805-12118,Ekstrand:2012:RFP:2365952.2366002}.
+Furthermore, a noteworthy shortcoming of the datasets constructed in the aforementioned publications is the usage of a metric which limits the choice of algorithms.
+The RMSE of the predicted and actual score is a popular metric but, e.g., can not be computed in a straight-forward way for content-based filtering algorithms.
 
@@
 The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}).
+In place of a metric, the recall in Top-N set is chosen as it can be computed for a wide range of algorithms.
 It is further amended with aggregated statistics about users and items and metadata of an exemplary experiment.
@@
 	\centering
-	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}
+	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}%
 	\label{tab:IllustrativeTable}
@@
 Furthermore, transactions containing no information about the user's location are dropped.
-Thereby enabling the consistent usage of a user’s location information in new approaches.
+Thereby enabling the consistent usage of a user's location information in new approaches.
 
@@
 
+The recall in a Top-N test set is used as score of how good an algorithm is able to recommend an item.
+\begin{enumerate*}[label= (\arabic*)]
+	\item For each user, first $100$ items with which the user has not interacted with are selected.
+	\item The algorithm is then requested to rank an item with which the user has interacted with but which was not used for building the user's profile and the $100$ randomly sampled items.
+It is assumed that the random $100$ items are of low interest to the user.
+	\item The position of the item with which the user has interacted with in the ranked test set may now be taken as the recall in a Top-N test set.
+\end{enumerate*}
+
 A classical 5-fold cross-validation on the users is applied for training the collaborative filters.
-Using the recall in a Top-N test set, a score of how good an algorithm is able to recommend an item is calculated.
-The algorithm is provided with all the items with which the user from the test set has interacted with except for one and is requested to create a ranking of $100$ random items with which the user has not interacted with plus the one with which an interaction has taken place.
 An ordering is assumed to be implied by the magnitudes of the values in the reconstructed matrix of the decomposition respectively the distance to the neighbor.
-The position of the interacted item in the set of $101$ items is then used as score for the user-item transaction.
+The validation process of the content-based approaches uses leave-one-out.
+The ranking is performed using the cosine similarity of an item's vector and the user's profile.
 
-The validation process of the content-based approaches uses leave-one-out.
-For each transaction a profile of the user is constructed which excludes this transaction.
-Afterwards, the algorithm is requested to create a ranking of $100$ items with which the user has not interacted with and the one with which a transaction has taken place.
-The ranking is performed using the cosine similarity of an item’s vector and the user's profile.
-
-The choice of evaluation method ensures that it can be applied to a vast set of different algorithms as long as a ranking of items can be produced and therefore allow for a high variety within the set of algorithms in the learning subsystem.
+The choice of evaluation method ensures that it can be applied to a vast set of different algorithms as long as a ranking of items can be produced.
+Therefore, it allow for a high variety within the set of algorithms in the learning subsystem in contrast to, e.g., RMSE.
 It further ensures that not just the ability to decompose the data is measured but the ability to recommend new items to users~\cite{Cremonesi:2010:PRA:1864708.1864721}.
@@
 The percentage below each algorithm indicates how often it is the best possible algorithm.
-To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}
+To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}%
 	\label{fig:MetaLearnerStatistics}
@@
 	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
-	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}
+	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}%
 	\label{fig:MetaLearnerPerformance}

### 2019-02-15 doc/paper/main.tex
paper/main.tex: Add citations and amendments
Adapt literature.bib accordingly.

@@
 \section{Introduction}
-Meta-Learning is the process of applying machine learning algorithms on metadata as is generated by a subsystem composed of machine learners.
-The goal of meta-learning systems is to improve existing approaches by combining the strengths of several single machine learning systems in an ensemble.
-In recommender systems it is an emerging field of interest as meta-learning promises to better sort through item, user and transaction information as to retrieve the best possible match of item and user.
+Meta-Learning is the process of applying machine learning algorithms on metadata as generated by a subsystem composed of machine learners.
+The goal of meta-learning systems is to improve existing approaches by combining the strengths of several single machine learning systems~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}.
+In recommender systems it is an emerging field of interest as meta-learning promises to better sort through item-, user- and transaction-information as to retrieve the best possible match of item and user.
+In order to investigate meta-learning algorithms, the required metadata needs to be computed in advance.
 
@@
 
-Our objective is to address the data augmentation part in a comprehensive way as to allow researchers to focus on the actual meta-learning evaluation.
+Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning evaluation.
 We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich, vast corpus is a suitable candidate.
 The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}).
-In place of a metric, the recall in Top-N set is chosen as it can be computed for a wide range of algorithms.
-It is further amended with aggregated statistics about users and items and metadata of an exemplary experiment.
+In place of a metric, the recall in a Top-N set is used as it can be computed for a wide range of algorithms.
+The dataset is further amended with aggregated statistics about users and items and metadata of an exemplary experiment.
 

### 2019-02-15 doc/paper/compact.tex
paper/compact.tex: Pull in changes from main.tex

--- 2019-02-15 doc/paper/main.tex
@@
 	\makeatother
-	\setlength{\intextsep}{1em}  % Reduce excessive spacing between float and text
-	\setlength{\textfloatsep}{1em}  % Reduce excessive spacing between caption and text
+	%\setlength{\intextsep}{1.1em}  % Reduce excessive spacing between float and text
+	%\setlength{\textfloatsep}{1.1em}  % Reduce excessive spacing between caption and text
 
@@
 
-\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
+%\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
 \title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
-\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1}}
-\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
-\institute{
-	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
-	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{G.Edenhofer@campus.lmu.de, collinsa@tcd.ie}
+\author{
+	\IEEEauthorblockN{
+		Gordian~Edenhofer\IEEEauthorrefmark{1}\IEEEauthorrefmark{2} and
+		Andrew~Collins\IEEEauthorrefmark{1}
 	}
 
+	\IEEEauthorblockA{
+		\IEEEauthorrefmark{1}Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland
+	}
+
+	\IEEEauthorblockA{
+		\IEEEauthorrefmark{2}National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan
+	}
+
+	\href{mailto:G.Edenhofer@campus.lmu.de}{G.Edenhofer@campus.lmu.de},
+	\href{mailto:collinsa@tcd.ie}{collinsa@tcd.ie}
+}
+%\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
+
 \maketitle  % Typeset the header of the contribution
-\markboth{}{}  % Clear the section and author from the page header
+%\markboth{}{}  % Clear the section and author from page headers
 
@@
 The augmented dataset and the source code are released into the public domain at GitHub:Edenhofer/Augmented-DonorsChoose.org-Dataset.
+\end{abstract}
 
-\keywords{recommender systems \and meta-learning \and dataset augmentation \and ensemble learning \and hybrid recommenders.}
-\end{abstract}
+\begin{IEEEkeywords}
+	recommender systems, meta-learning, dataset augmentation, ensemble learning, hybrid recommenders.
+\end{IEEEkeywords}
 
@@
 
-\begin{table}[ht]
+\begin{table*}[ht]
 	\centering
-	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}%
+	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}
 	\label{tab:IllustrativeTable}
 	\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/Illustrative example of the overall design of the augmented transaction table}}}
-\end{table}
+\end{table*}
 
@@
 	}
-	\caption{The frequency of the number of interactions per user without outliers is shown in~\subref{fig:InteractionFrequency} and the distribution of the transformed interaction strength is shown in~\subref{fig:InteractionStrength}.}\label{fig:Interactions}
+	\caption{The frequency of the number of interactions per user without outliers is shown in~\subref{fig:InteractionFrequency} and the distribution of the transformed interaction strength is shown in~\subref{fig:InteractionStrength}.}%
+	\label{fig:Interactions}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
+	\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
 	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}%

### 2019-02-15 doc/paper/compact.tex
paper/main.tex: Minor corrections and linking
Update paper/compact.tex accordingly.

@@
 The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set.
-The augmented dataset and the source code are released into the public domain at GitHub:Edenhofer/Augmented-DonorsChoose.org-Dataset.
+The augmented dataset and the source code are released into the public domain at \href{https://github.com/Edenhofer/Augmented-DonorsChoose.org-Dataset}{GitHub:Edenhofer/Augmented-DonorsChoose.org-Dataset}.
 \end{abstract}
@@
 Multiple examples of manual and repetitious data augmentation may be found in the scientific literature, for instance in~\cite{CUNHA2018128,DBLP:journals/corr/abs-1805-12118,Ekstrand:2012:RFP:2365952.2366002}.
-Furthermore, a noteworthy shortcoming of the datasets constructed in the aforementioned publications is the usage of a metric which limits the choice of algorithms.
+Furthermore, a noteworthy shortcoming of the metadata constructed in the aforementioned publications is the usage of a metric which limits the choice of algorithms.
 The RMSE of the predicted and actual score is a popular metric but, e.g., can not be computed in a straight-forward way for content-based filtering algorithms.

### 2019-02-15 doc/paper/main.tex
paper/main.tex: Minor corrections and linking
Update paper/compact.tex accordingly.

@@
 The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set.
-The augmented dataset and the source code are released into the public domain at GitHub:Edenhofer/Augmented-DonorsChoose.org-Dataset.
+The augmented dataset and the source code are released into the public domain at \href{https://github.com/Edenhofer/Augmented-DonorsChoose.org-Dataset}{GitHub:Edenhofer/Augmented-DonorsChoose.org-Dataset}.
 

### 2019-03-31 doc/paper/main.tex
paper/main.tex: Shorten and tweak choice of words

@@
 \section{Introduction}
-Meta-Learning is the process of applying machine learning algorithms on metadata as generated by a subsystem composed of machine learners.
-The goal of meta-learning systems is to improve existing approaches by combining the strengths of several single machine learning systems~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}.
-In recommender systems it is an emerging field of interest as meta-learning promises to better sort through item-, user- and transaction-information as to retrieve the best possible match of item and user.
+Meta-Learning is the process of applying machine learning algorithms on metadata of previous machine learning experiments.
+The goal is to improve existing approaches by combining the strengths of several single machine learning systems~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}.
+In recommender systems it is an emerging field of interest as meta-learning promises to utilize patterns in metadata as to retrieve the best possible match of item and user.
 In order to investigate meta-learning algorithms, the required metadata needs to be computed in advance.
@@
 Multiple examples of manual and repetitious data augmentation may be found in the scientific literature, for instance in~\cite{CUNHA2018128,DBLP:journals/corr/abs-1805-12118,Ekstrand:2012:RFP:2365952.2366002}.
-Furthermore, a noteworthy shortcoming of the metadata constructed in the aforementioned publications is the usage of a metric which limits the choice of algorithms.
-The RMSE of the predicted and actual score is a popular metric but, e.g., can not be computed in a straight-forward way for content-based filtering algorithms.
+Furthermore, the choice of the metric for computing metadata in the system of single machine learners is important.
+Using the RMSE, as is done in some of the aforementioned publications, disallows using content-based methods.
 
-Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning evaluation.
-We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich, vast corpus is a suitable candidate.
+Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning task.
+We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich and vast corpus is a suitable candidate.
 The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}).
@@
 
-The corpus features comprehensive information on the users~(donors), items~(projects) and transactions respectively interactions~(donations).
-Transactions are represented by an interaction of a user with an item at a specific point in time and further include a strength~(amount~donated).
+The corpus features comprehensive information on the users (donors), items (projects) and transactions respectively interactions (donations).
+Transactions are represented by an interaction of a user with an item at a specific point in time and further include a strength (amount~donated).
 Users feature information about their location and a boolean value indicating whether they are a teacher.
@@
 
-In a learning subsystem step, two collaborative filtering techniques and two content-based filtering techniques are applied.
+The learning subsystem comprises two collaborative filtering techniques and two content-based filtering techniques.
 The performance measures of the single algorithms are amended to the table.
@@
 The choice of evaluation method ensures that it can be applied to a vast set of different algorithms as long as a ranking of items can be produced.
-Therefore, it allow for a high variety within the set of algorithms in the learning subsystem in contrast to, e.g., RMSE.
+Therefore, it allows for a high variety within the set of algorithms in the learning subsystem in contrast to, e.g., RMSE.
 It further ensures that not just the ability to decompose the data is measured but the ability to recommend new items to users~\cite{Cremonesi:2010:PRA:1864708.1864721}.
@@
 The third meta-learner is a classical stacking ensemble using a decision tree which is given the prediction from the learning subsystem as additional input.
-Based on the metadata and the output of the learning subsystem, it then performs a transaction classification.
+Based on that, it performs a transaction classification.
 The final approach aims at solving the ASP via clustering transactions based on the meta-features using K-Means and assigns clusters an overall best algorithm via majority voting.
@@
 
-The requirement enforcing users to have interacted at least twice results in a distribution of the number of users interacting with items which decays exponentially as depicted in~\autoref{fig:InteractionFrequency}.
-This is to be expected as the time users can invest in researching items and their total interaction strength (budget) is limited.
+Requiring users to have interacted at least twice, results in a distribution of the number of interactions per user which decays exponentially as depicted in~\autoref{fig:InteractionFrequency}.
+This is to be expected as the time and interaction strength (budget) a user can invest is limited.
 The dataset is dominated by users which interacted exactly two times.
@@
 SVD performs better but is still unable to reliably yield good recommendations.
-Furthermore, grouping users by shared item interactions has no observable positive impact on the recommendation of new items.
+Grouping users by shared item interactions has no observable positive impact on the recommendation.
 

### 2019-03-31 doc/paper/main.tex
paper/main.tex: Drop page-count
Furthermore, comment out some unenforced `\setlength` command.
paper/main.tex: Readd supervisors and BeelGroup

@@
 	\setlength{\intextsep}{1em}  % Reduce excessive spacing between float and text
-	\setlength{\textfloatsep}{1em}  % Reduce excessive spacing between caption and text
+	%\setlength{\textfloatsep}{1em}  % Reduce excessive spacing between caption and text
 
@@
 	\captionsetup{subrefformat=bold}
+
+	\pagenumbering{gobble}  % Disable page-numbering
 
@@
 \titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
-\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
-\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1}}
+\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
+	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}}
+\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
 \authorrunning{G. Edenhofer et al.}  % Abbreviated author field
@@
 	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
-	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{G.Edenhofer@campus.lmu.de, collinsa@tcd.ie}
+	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, collinsa@tcd.ie, aizawa@nii.ac.jp}
 }
@@
 The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set.
-The augmented dataset and the source code are released into the public domain at \href{https://github.com/Edenhofer/Augmented-DonorsChoose.org-Dataset}{GitHub:Edenhofer/Augmented-DonorsChoose.org-Dataset}.
+The augmented dataset and the source code are released into the public domain at \href{https://github.com/BeelGroup/Augmented-DonorsChoose.org-Dataset}{GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset}.
 

### 2019-03-31 doc/paper/main.tex
paper/main.tex: Add graphics
Add visuals to the resource folder "doc/res". Furthermore, give the
files names which do not contain any special characters.

@@
 	\label{tab:IllustrativeTable}
-	\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/Illustrative example of the overall design of the augmented transaction table}}}
+	\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/table}}}
 \end{table}
@@
 	\subcaptionbox{Interactions Frequency\label{fig:InteractionFrequency}}{
-		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/DonorID - Distribution of number of interactions per user}}}
+		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/number_interactions}}}
 	}
@@
 	\subcaptionbox{Interaction Strength\label{fig:InteractionStrength}}{
-		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/DonationAmount - Distribution of ratings for logarithmic bins and excluded outliers}}}
+		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/distribtion_ratings}}}
 	}
@@
 	\centering
-	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Learning subsystem - Position in Top-N test set}}}
+	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/learning_subsystem_position}}}
 	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem.
@@
 	\centering
-	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
+	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/meta_learner_performance_average_position}}}
 	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}%

### 2019-03-31 doc/paper/main.tex
paper/main.tex: Grammar and wording details

@@
 In the augmentation, metadata of collaborative and content-based filtering techniques is amended to the corpus.
-It is further extended with aggregated statistics for users and transactions and an exemplary meta-learning experiment.
+It is further extended with aggregated statistics of users and transactions and an exemplary meta-learning experiment.
 The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set.
@@
 Multiple examples of manual and repetitious data augmentation may be found in the scientific literature, for instance in~\cite{CUNHA2018128,DBLP:journals/corr/abs-1805-12118,Ekstrand:2012:RFP:2365952.2366002}.
-Furthermore, the choice of the metric for computing metadata in the system of single machine learners is important.
+Furthermore, the choice of the metric for computing metadata of single machine learners is important.
 Using the RMSE, as is done in some of the aforementioned publications, disallows using content-based methods.
@@
 In place of a metric, the recall in a Top-N set is used as it can be computed for a wide range of algorithms.
-The dataset is further amended with aggregated statistics about users and items and metadata of an exemplary experiment.
+The dataset is further amended with aggregated statistics about users and items, and metadata of an exemplary experiment.
 
@@
 
-The learning subsystem comprises two collaborative filtering techniques and two content-based filtering techniques.
+In a first step, two collaborative filtering techniques and two content-based filtering techniques are applied.
 The performance measures of the single algorithms are amended to the table.
@@
 Internal stop words in description strings of items are stripped.
-Furthermore, transactions containing no information about the user's location are dropped.
-Thereby enabling the consistent usage of a user's location information in new approaches.
+Furthermore, transactions containing no information about the user's location are dropped thereby enabling the consistent usage of a user's location information in new approaches.
 
@@
 Lastly, the donated amount is transformed to a transaction strength in the range of unity to five in analogy to a rating score.
-This step reduces the influence of outliers respectively unusual donated amounts.
+This step reduces the influence of outliers respectively uncommon donated amounts.
 
@@
 The learning subsystem is a recommender system itself.
-SVD and KNN are used as representatives for collaborative filtering techniques and TF-IDF and word-embedding for content-based filters~\cite{scikit-learn,rehurek_lrec}.
+SVD and KNN are used as representatives for collaborative filtering techniques and TF-IDF and word-embedding as content-based filters~\cite{scikit-learn,rehurek_lrec}.
 Hereby, the otherwise intrinsic inductive bias is reduced.
@@
 A classical 5-fold cross-validation on the users is applied for training the collaborative filters.
-An ordering is assumed to be implied by the magnitudes of the values in the reconstructed matrix of the decomposition respectively the distance to the neighbor.
+An ordering is assumed to be implied by the magnitudes of the values in the reconstructed matrix of the decomposition respectively the distances to the neighbors.
 The validation process of the content-based approaches uses leave-one-out.
@@
 \subsection{Statistics and Application of Learning Subsystem}
-The meta-learning system processes the metadata from the learning subsystem and further statistics.
+The meta-learning system processes the metadata of the learning subsystem and further statistics.
 Its performance is evaluated via a holdout split on the transaction table using $80\%$ for training and the rest for testing.
@@
 
-Four different meta-learning approaches are discussed which address the Algorithm Selection Problem (ASP) via a switching hybrid ensemble.
+Four different meta-learning approaches are discussed which address the Algorithm Selection Problem (\textbf{ASP}) via a switching hybrid ensemble.
 The aim of the system is to predict the algorithm with the lowest recall-position for each transaction respectively each row in~\autoref{tab:IllustrativeTable}.
@@
 	\centering
-	\subcaptionbox{Interactions Frequency\label{fig:InteractionFrequency}}{
+	\subcaptionbox{Interaction Frequency\label{fig:InteractionFrequency}}{
 		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/number_interactions}}}
@@
 
-That the stacking ensemble performs best is unsurprising as it is provided significantly more information than the other algorithms.
+The fact that the stacking ensemble performs best is unsurprising as it is provided significantly more information than the other algorithms.
 The performance of the gradient booster is encouraging as it successfully addresses the ASP.
@@
 Aggregated user and item statistics are amended to the table.
-Metadata of four switching hybrid ensemble meta-learners is amended to the dataset.
+Furthermore, Metadata of four switching hybrid ensemble meta-learners is amended to the dataset.
 The augmented public domain dataset lays the groundwork that future evaluations of existing and novel meta-learning approaches can build upon.

### 2019-04-03 doc/poster/main.tex
doc: Add a poster
Add the required logos to the "res/" folder.

--- 2019-03-31 doc/paper/main.tex
@@
-\documentclass[runningheads]{llncs}
+\documentclass[final]{beamer}
+\usepackage[orientation=portrait,size=a0,scale=1.425,debug]{beamerposter} % Format beamer as poster
+
 \usepackage[ngerman,english]{babel}  % Language specification
@@
 \usepackage{multirow}
-	\usepackage{ellipsis}
-	\usepackage{textcomp}
-	\usepackage{longtable}
-	\usepackage{rotating}
-	\usepackage[section]{placeins}
 
@@
 
-	\usepackage[style=numeric,sorting=none,backend=biber]{biblatex}  % Reference manager
-	\usepackage[bookmarks]{hyperref}  % Clickable references
+\usepackage[backend=biber,style=numeric,sorting=none,giveninits=true,doi=false,isbn=false,url=false,eprint=false]{biblatex}  % Reference manager
+\usepackage{csquotes}		% Ensure proper quotation of texts with babel and polyglossia with biblatex
+\usepackage{hyperref}		% Insert clickable references
 
@@
 
+\AtBeginBibliography{\footnotesize}
 \addbibresource{../literature.bib}
 
-	% Display URLs in blue roman font if using hyperref to comply with Springer's eBook style
-	\renewcommand\UrlFont{\color{blue}\rmfamily}
+\setbeamertemplate{navigation symbols}{}
 
-	\makeatletter
-	% Insert a float barrier before subsections just like the package 'placeins' does for sections
-	%\AtBeginDocument{%
-	%	\expandafter\renewcommand\expandafter\subsection\expandafter{%
-	%		\expandafter\@fb@secFB\subsection
-	%	}%
-	%}
-	\makeatother
-	\setlength{\intextsep}{1em}  % Reduce excessive spacing between float and text
-	%\setlength{\textfloatsep}{1em}  % Reduce excessive spacing between caption and text
+% Prettify poster
+\definecolor{BlockTitle}{RGB}{32, 113, 182}
+\definecolor{BlockBg}{RGB}{230, 230, 230}
+\usefonttheme[onlymath]{serif}%
+\setbeamercolor*{title}{fg = black}%
+\setbeamercolor*{title page}{fg = black}%
+\setbeamercolor*{block title}{fg = BlockTitle, bg = BlockBg}%
+\setbeamercolor*{caption name}{fg = black}%
+\setbeamercolor*{bibliography entry author}{fg = black}%
+\setbeamercolor*{bibliography entry title}{fg = black}%
+\setbeamercolor*{bibliography entry location}{fg = black}%
+\setbeamercolor*{bibliography entry note}{fg = black}%
+\setbeamerfont{title}{series = \bfseries}%
+\setbeamerfont{institute}{size = \small}%
+\setbeamertemplate{caption}[numbered]%
+\setbeamertemplate{caption label separator}[endash]%
+\setbeamertemplate{bibliography item}[text]
+%\usebackgroundtemplate{\includegraphics[width=\paperwidth,height=\paperheight]{./MUW_green.pdf}}  % Background image
 
-	% Use bold sub-caption references
-	\DeclareCaptionLabelFormat{bold}{\textbf{#2}}
-	\captionsetup{subrefformat=bold}
+\captionsetup{font=small,skip=0em}  % Move caption close to figure and or graphic
 
-	\pagenumbering{gobble}  % Disable page-numbering
-
-	%\parindent0em  % Indentation of the first line of a paragraph
-	\newcommand{\leadingzero}[1]{\ifnum#1<10 0\the#1\else\the#1\fi}
-	\newcommand{\todayddmmyyyy}{\leadingzero{\day}.\leadingzero{\month}.\the\year}
-	\newcommand{\mathcolorbox}[2]{\colorbox{#1}{$\displaystyle #2$}}
-	\renewcommand{\sectionautorefname}{\ifnum\spacefactor>1000 Section\else section\fi}  % Capitalize 'section' if used after some spacing
-	\def\permille{\ensuremath{{}^\text{o}\mkern-5mu/\mkern-3mu_\text{oo}}}  % Permille sign
-
-	\lstset{basicstyle=\ttfamily,breaklines=true}  % Prettier code highlighting style
-	\pagestyle{myheadings}  % Prettier page format with header but without footer
+\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
+\subject{Algorithm Selection and Meta-Learning in Information Retrieval}
+\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
+\institute{%
+\inst{1}Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\
+\inst{2}National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan
+\and \href{mailto:beelj@tcd.ie}{beelj@tcd.ie}, \href{mailto:collinsa@tcd.ie}{collinsa@tcd.ie}, \href{mailto:aizawa@nii.ac.jp}{aizawa@nii.ac.jp}
+}
+\date{}  % Set date to nothing
 
@@
 
-\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
-\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
-	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}}
-\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
-\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
-\institute{
-	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
-	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, collinsa@tcd.ie, aizawa@nii.ac.jp}
-}
+\begin{frame}[t,fragile=singleslide]{}
+	% Headline
+	\begin{columns}[t]
+		\begin{column}{0.02\textwidth}
+		\end{column}
 
-\maketitle  % Typeset the header of the contribution
-\markboth{}{}  % Clear the section and author from the page header
+		\begin{column}{0.18\textwidth}
+			\flushleft%
+			\vspace{1em}
+			\includegraphics[width=0.8\columnwidth]{{{../res/Logo of Trinity College Dublin}}}
+		\end{column}
 
-\begin{abstract}
+		\begin{column}{0.6\textwidth}
+			\vspace{1em}
+			\titlepage%
+		\end{column}
+
+		\begin{column}{0.18\textwidth}
+			\flushright%
+			\vspace{1em}
+			\vspace{2em}\includegraphics[width=0.8\columnwidth]{{{../res/Logo of NII}}}
+		\end{column}
+
+		\begin{column}{0.02\textwidth}
+		\end{column}
+	\end{columns}
+
+	\begin{columns}[t]
+		\begin{column}{0.45\textwidth}
+			\begin{block}{Abstract}
 				The DonorsChoose.org dataset of past donations provides a big and feature-rich corpus of users and items.
@@
 The augmented dataset and the source code are released into the public domain at \href{https://github.com/BeelGroup/Augmented-DonorsChoose.org-Dataset}{GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset}.
+			\end{block}
 
-\keywords{recommender systems \and meta-learning \and dataset augmentation \and ensemble learning \and hybrid recommenders.}
-\end{abstract}
+			\begin{block}{Introduction}
+				Meta-Learning is the process of applying machine learning on metadata of previous machine learning experiments.
+The goal is to improve existing approaches by combining the strengths of several single machine learnings~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}.
+The metadata though needs to be computed in advance.
 
-\section{Introduction}
-Meta-Learning is the process of applying machine learning algorithms on metadata of previous machine learning experiments.
-The goal is to improve existing approaches by combining the strengths of several single machine learning systems~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}.
-In recommender systems it is an emerging field of interest as meta-learning promises to utilize patterns in metadata as to retrieve the best possible match of item and user.
-In order to investigate meta-learning algorithms, the required metadata needs to be computed in advance.
-
-One challenge for researchers interested in meta-learning is that suitable datasets are time-consuming and cumbersome to construct.
-Creating a system of individual machine learning experiments and amending their metadata to the original corpus takes time and resources away from working with the actual meta-learners.
 				Multiple examples of manual and repetitious data augmentation may be found in the scientific literature, for instance in~\cite{CUNHA2018128,DBLP:journals/corr/abs-1805-12118,Ekstrand:2012:RFP:2365952.2366002}.
@@
 				Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning task.
-We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich and vast corpus is a suitable candidate.
-The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}).
-In place of a metric, the recall in a Top-N set is used as it can be computed for a wide range of algorithms.
-The dataset is further amended with aggregated statistics about users and items, and metadata of an exemplary experiment.
+We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich and vast corpus is suitable.
+			\end{block}
+		\end{column}
 
-\section{Methodology}
+		\begin{column}{0.45\textwidth}
+			\begin{block}{Methodology}
+				The DonorsChoose.org dataset is composed of past donations featuring $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects.
+The corpus provides significantly more transactions with more detailed item and transaction information compared to, e.g., the popular MovieLens dataset.
+An exemplary itemized view of the augmented dataset is shown in~\autoref{tab:IllustrativeTable} with the augmented data to the right of the separator.
 
-\subsection{The Dataset}
-DonorsChoose.org is an organization which enables teachers to file project requests for resources for their school.
-Collectively the nonprofit has raised $\$685$ million for classrooms in the United States of America.
-Their dataset composed of past donations features $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects.
-The corpus provides significantly more transactions with more detailed item and transaction information compared to, e.g., the popular MovieLens dataset.
-An exemplary itemized view of the augmented dataset is shown in~\autoref{tab:IllustrativeTable}.
-
-The corpus features comprehensive information on the users (donors), items (projects) and transactions respectively interactions (donations).
-Transactions are represented by an interaction of a user with an item at a specific point in time and further include a strength (amount~donated).
-Users feature information about their location and a boolean value indicating whether they are a teacher.
-Items feature multiple textual descriptions, funding goals, a list of associated categories and types, information about the creator and details about the location of the school which the item is about.
-
-In a first step, two collaborative filtering techniques and two content-based filtering techniques are applied.
-The performance measures of the single algorithms are amended to the table.
-Next, aggregated user and item statistics are calculated and added to the table.
-Lastly, four exemplary meta-learners are applied and the performance measures of the individual approaches are added to the corpus.
-
+				\vspace*{-.5\baselineskip}  % TODO: Fix this HACK
 				\begin{table}[ht]
 					\centering
-	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}%
-	\label{tab:IllustrativeTable}
 					\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/table}}}
+					\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}\label{tab:IllustrativeTable}
 				\end{table}
 
-\subsection{Dataset Preparation}
-To prepare the dataset for evaluations, duplicate interactions are merged as the recommender systems shall not recommend items to which the user has already donated to.
-Internal stop words in description strings of items are stripped.
-Furthermore, transactions containing no information about the user's location are dropped thereby enabling the consistent usage of a user's location information in new approaches.
-
-Additionally, users having interacted less than twice are removed as well.
-Although, this limits the target group, the step is unavoidable as the employed validation process requires at least one interaction per user for testing and one for training.
-The evaluation requires user profiles and hence training-transactions in order to recommend new items which in turn need to be validated against test-transactions.
-Lastly, the donated amount is transformed to a transaction strength in the range of unity to five in analogy to a rating score.
-This step reduces the influence of outliers respectively uncommon donated amounts.
-
-\subsection{Learning Subsystem}
-The learning subsystem is a recommender system itself.
 				SVD and KNN are used as representatives for collaborative filtering techniques and TF-IDF and word-embedding as content-based filters~\cite{scikit-learn,rehurek_lrec}.
@@
 				\end{enumerate*}
+			\end{block}
+		\end{column}
+	\end{columns}
 
-A classical 5-fold cross-validation on the users is applied for training the collaborative filters.
-An ordering is assumed to be implied by the magnitudes of the values in the reconstructed matrix of the decomposition respectively the distances to the neighbors.
-The validation process of the content-based approaches uses leave-one-out.
-The ranking is performed using the cosine similarity of an item's vector and the user's profile.
-
-The choice of evaluation method ensures that it can be applied to a vast set of different algorithms as long as a ranking of items can be produced.
-Therefore, it allows for a high variety within the set of algorithms in the learning subsystem in contrast to, e.g., RMSE.
-It further ensures that not just the ability to decompose the data is measured but the ability to recommend new items to users~\cite{Cremonesi:2010:PRA:1864708.1864721}.
-Hereby, the learning subsystem is kept extensible while still providing useful metadata to meta-learning algorithms.
-
-\subsection{Statistics and Application of Learning Subsystem}
-The meta-learning system processes the metadata of the learning subsystem and further statistics.
-Its performance is evaluated via a holdout split on the transaction table using $80\%$ for training and the rest for testing.
-Transactions are expanded to contain more detailed information about the time, the user's location and aggregated statistics about the mean of the categories, location and interaction-strength of items with which the user has interacted with.
-Statistics are solely based on the training set.
-Values for unknown users are filled with the mean in the training data.
-
-Four different meta-learning approaches are discussed which address the Algorithm Selection Problem (\textbf{ASP}) via a switching hybrid ensemble.
-The aim of the system is to predict the algorithm with the lowest recall-position for each transaction respectively each row in~\autoref{tab:IllustrativeTable}.
-The overall performance of a meta-learner is measured using the mean recall-position for when the recommended algorithm for each transaction is used.
-
-The first approach aims at predicting the algorithm which will best describe the transaction via a classification based on the given meta-features using a decision tree.
-The second approach employs a gradient boosting regressor to predict the position of the recall for each transaction and for each algorithm in the learning subsystem separately.
-As best algorithm, the one with the lowest predicted recall-position is chosen.
-
-The third meta-learner is a classical stacking ensemble using a decision tree which is given the prediction from the learning subsystem as additional input.
-Based on that, it performs a transaction classification.
-The final approach aims at solving the ASP via clustering transactions based on the meta-features using K-Means and assigns clusters an overall best algorithm via majority voting.
-
-\section{Results}
+	\begin{columns}[t]
+		\begin{column}{0.945\textwidth}
+			\begin{block}{Results}
+				\begin{columns}[t]
+					\begin{column}{0.49\textwidth}
 						The preparation of the dataset preserves a little more than half of the data with the most notable drop in the number of transactions being introduced by requiring users to have donated at least twice.
 The sample of $100,000$ transactions contains $18,735$ unique users and $88,100$ unique projects.
+The decay of the interaction frequency is seen in~\autoref{fig:InteractionFrequency}, the distribution of interaction strength in~~\autoref{fig:InteractionStrength}.
 
@@
 							}
-	\hspace{2em}
+							\hspace{.5em}
 							\subcaptionbox{Interaction Strength\label{fig:InteractionStrength}}{
@@
 						\end{figure}
+					\end{column}
 
-Requiring users to have interacted at least twice, results in a distribution of the number of interactions per user which decays exponentially as depicted in~\autoref{fig:InteractionFrequency}.
-This is to be expected as the time and interaction strength (budget) a user can invest is limited.
-The dataset is dominated by users which interacted exactly two times.
-
-The distribution of the transformed interaction strength in analogy to a rating score is shown in~\autoref{fig:InteractionStrength}.
-It peaks at the second highest score.
-Interactions with a weak to medium interaction strength and ones with the strongest interaction strength are about equally likely.
-Interactions with the lowest strength value are very infrequent.
+					\begin{column}{0.49\textwidth}
+						Statistical information about the performances of the individual machine learners in the learning subsystem are visualized in~\autoref{fig:MetaLearnerStatistics}.
+Overall, content-based filters are significantly better in achieving a low recall-position.
+The baseline is set to be the single best algorithm, i.e., TF-IDF.
+As seen in~\autoref{fig:MetaLearnerPerformance}, the baseline is beaten by two meta-learners.
 
@@
 							\centering
-	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/learning_subsystem_position}}}
-	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem.
+							\subcaptionbox{Statistics\label{fig:MetaLearnerStatistics}}{
+								\includegraphics[width=.45\textwidth,height=\textheight,keepaspectratio]{{{../res/learning_subsystem_position}}}
+							}
+							\hspace{.5em}
+							\subcaptionbox{Perfromance\label{fig:MetaLearnerPerformance}}{
+								\includegraphics[width=.45\textwidth,height=\textheight,keepaspectratio]{{{../res/meta_learner_performance_average_position}}}
+							}
+							\caption{Statistical features of the distributions of the recall-positions of the learning subsystem are shown in~\subref{fig:MetaLearnerStatistics}.
 The dashed green lines indicate the mean, the straight orange lines the median.
 The percentage below each algorithm indicates how often it is the best possible algorithm.
-To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}%
-	\label{fig:MetaLearnerStatistics}
+To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.
+							The performance of the meta-learner system addressing the ASP is shown in~\subref{fig:MetaLearnerPerformance}.
+The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}\label{fig:MetaLearner}
 						\end{figure}
+					\end{column}
+				\end{columns}
+			\end{block}
+		\end{column}
+	\end{columns}
 
-Statistical information about the performances are visualized in~\autoref{fig:MetaLearnerStatistics}.
-It can be observed that the performance of the learning subsystem depends highly on the employed filtering techniques.
-Overall, content-based filters are significantly better in achieving a low recall-position (average position in Top-N set; content-based filtering:~$19.48$, collaborative filtering:~$83.28$).
-The algorithm with the poorest performance is KNN.
-SVD performs better but is still unable to reliably yield good recommendations.
-Grouping users by shared item interactions has no observable positive impact on the recommendation.
-
-Considering the low average number of interactions per user and the vast number of items available, KNN apparently fails to find appropriate neighbors.
-SVD seems to struggle with the sparsity of the input matrix as looking at the reconstruction of the decomposed matrix it is revealed that most values are well below unity and very similar to each other.
-SVD yields recall-positions below $10$ infrequently.
-
-Content-based filtering techniques achieve better performance scores on the dataset.
-User profiles based on TF-IDF and fastText each yield recall-positions below $10$ for roughly half of all transactions with the simpler TF-IDF performing slightly better than fastText.
-This could be at least in part due to users explicitly searching for specific terms instead of exploring all possible items manually.
-
-Between the different meta-learning approaches, significant changes in the mean recall-position can be noted as seen in~\autoref{fig:MetaLearnerPerformance}.
-The worst performer is the user-clustering using K-Means (average position in Top-N:~$15.56$).
-The stacking decision tree performs best (average position in Top-N:~$9.02$).
-Of the three non-stacking approaches the gradient booster performs best (average position in Top-N:~$11.21$) and achieves a better score than the single best algorithm, i.e., TF-IDF (average position in Top-N:~$11.96$).
-The classifying decision tree (average position in Top-N:~$15.27$) outperforms the user-clustering but is still notably worse than the overall best algorithm.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/meta_learner_performance_average_position}}}
-	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}%
-	\label{fig:MetaLearnerPerformance}
-\end{figure}
-
-The fact that the stacking ensemble performs best is unsurprising as it is provided significantly more information than the other algorithms.
-The performance of the gradient booster is encouraging as it successfully addresses the ASP.
-From the poor performance of the user-clustering it can be reasoned that similar transactions do not necessarily yield similar results using the same recommender algorithm.
-Hence, the similarity of meta-feature does not imply that the performance of recommendations is similar.
-
-The classification and error prediction approach apparently suffer from the level of indirection which is introduced by predicting a single algorithm and disregarding the penalty which is introduced if a bad performing one is chosen.
-Even a high accuracy in algorithm selection does not guarantee a low mean recall-position.
-This is partly mitigated by the error prediction approach but still not completely suppressed.
-
-\section{Conclusion}
+	\begin{columns}[t]
+		\begin{column}{0.45\textwidth}
+			\begin{block}{Conclusion}
 				The study provides an extensively augmented dataset based on the transaction data published by DonorsChoose.org.
@@
 The augmented public domain dataset lays the groundwork that future evaluations of existing and novel meta-learning approaches can build upon.
+			\end{block}
 
-\begin{appendix}
-	\printbibliography[heading=bibintoc]
-\end{appendix}
+			\begin{block}{Acknoledgement}
+				\footnotesize
+				This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.
+			\end{block}
+		\end{column}
+
+		\begin{column}{0.45\textwidth}
+			\begin{block}{References}
+				\printbibliography[heading=none]
+			\end{block}
+		\end{column}
+	\end{columns}
+\end{frame}
 

### 2019-04-08 doc/poster/main.tex
poster/main.tex: Redesign layout and shorten body
Shorten the text in the body of the poster, change the look
significantly and adapt countless smaller things to make the poster look
proper.

Prune dropped images and add the logo of the ADAPT group to the "res/"
folder instead.

@@
 
-\usepackage[inline]{enumitem}  % Inline enumeration capability
 \usepackage[font=small,labelfont=bf]{caption}  % Customize caption aesthetics
-\usepackage[font=small]{subcaption}  % Customize sub-captions
+\usepackage[subrefformat=parens,labelformat=parens,font=small]{subcaption}  % Customize sub-captions
 
@@
 
+\captionsetup{font=small,skip=0em}  % Move caption close to figure and or graphic
+
+\newcommand{\mathcolorbox}[2]{\colorbox{#1}{$\displaystyle #2$}}
+\newcommand{\parvspace}[1]{\vspace{.5em}}  % Manually HACK space after a paragraph
+
 \setbeamertemplate{navigation symbols}{}
@@
 % Prettify poster
-\definecolor{BlockTitle}{RGB}{32, 113, 182}
-\definecolor{BlockBg}{RGB}{230, 230, 230}
+\definecolor{TrinityBlue}{RGB}{32, 113, 182}
 \usefonttheme[onlymath]{serif}%
-\setbeamercolor*{title}{fg = black}%
+\setbeamerfont{title}{size=\LARGE}
+\setbeamercolor*{title}{fg = white}%
+\setbeamercolor*{author}{fg = white}%
+\setbeamercolor*{institute}{fg = white}%
+\setbeamercolor*{date}{fg = white}%
 \setbeamercolor*{title page}{fg = black}%
-\setbeamercolor*{block title}{fg = BlockTitle, bg = BlockBg}%
+\setbeamercolor*{item}{fg = black}%
+\setbeamercolor*{block title}{fg = TrinityBlue}%
 \setbeamercolor*{caption name}{fg = black}%
+\setbeamercolor*{bibliography item}{fg = black}
 \setbeamercolor*{bibliography entry author}{fg = black}%
@@
 \setbeamerfont{institute}{size = \small}%
+\setbeamertemplate{bibliography item}[text]
 \setbeamertemplate{caption}[numbered]%
 \setbeamertemplate{caption label separator}[endash]%
-\setbeamertemplate{bibliography item}[text]
 %\usebackgroundtemplate{\includegraphics[width=\paperwidth,height=\paperheight]{./MUW_green.pdf}}  % Background image
-
-\captionsetup{font=small,skip=0em}  % Move caption close to figure and or graphic
 
@@
 }
-\date{}  % Set date to nothing
+\date{\itshape{} Algorithm Selection and Meta-Learning in Information Retrieval (AMIR)}  % Set date to venue
 
@@
 	% Headline
+	\colorbox{TrinityBlue}{
+		\hspace{-1.02em}  % Ugly HACK to center background block around header and avoid "overfull \hbox" message
 		\begin{columns}[t]
-		\begin{column}{0.02\textwidth}
+			\begin{column}{0.01\textwidth}
 			\end{column}
@@
 				\vspace{1em}
-			\includegraphics[width=0.8\columnwidth]{{{../res/Logo of Trinity College Dublin}}}
+				\includegraphics[width=0.75\columnwidth]{{{../res/Logo of Trinity College Dublin}}}
 			\end{column}
 
-		\begin{column}{0.6\textwidth}
+			\begin{column}{0.5\textwidth}
 				\vspace{1em}
-			\titlepage%
+				\titlepage{}
 			\end{column}
@@
 				\vspace{1em}
-			\vspace{2em}\includegraphics[width=0.8\columnwidth]{{{../res/Logo of NII}}}
+				\vspace{2em}\includegraphics[width=0.8\columnwidth]{{{../res/Logo of ADAPT}}}
 			\end{column}
 
-		\begin{column}{0.02\textwidth}
+			\begin{column}{0.01\textwidth}
 			\end{column}
 		\end{columns}
+	}
+	\vspace{0.em}  % HACK to leave some space between the header and the content
 
@@
 		\begin{column}{0.45\textwidth}
-			\begin{block}{Abstract}
-				The DonorsChoose.org dataset of past donations provides a big and feature-rich corpus of users and items.
-The dataset matches donors to projects in which they might be interested in and hence is intrinsically about recommendations.
-Due to the availability of detailed item-, user- and transaction-features, this corpus represents a suitable candidate for meta-learning approaches to be tested.
-This study aims at providing an augmented corpus for further recommender systems studies to test and evaluate meta-learning approaches.
-In the augmentation, metadata of collaborative and content-based filtering techniques is amended to the corpus.
-It is further extended with aggregated statistics of users and transactions and an exemplary meta-learning experiment.
-The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set.
-The augmented dataset and the source code are released into the public domain at \href{https://github.com/BeelGroup/Augmented-DonorsChoose.org-Dataset}{GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset}.
+			\begin{block}{}
+			The augmented dataset and the source code are released into the public domain at \colorbox{yellow}{\bfseries \href{https://github.com/BeelGroup/Augmented-DonorsChoose.org-Dataset}{GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset}}.
+Each feature worthy of an explanation is described in the repository.
 			\end{block}
+			\vspace{1.5em}
 
@@
 				Meta-Learning is the process of applying machine learning on metadata of previous machine learning experiments.
-The goal is to improve existing approaches by combining the strengths of several single machine learnings~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}.
+The goal is to improve existing approaches by combining the strengths of several single machine learners.
 The metadata though needs to be computed in advance.
+				\parvspace{}
 
@@
 Using the RMSE, as is done in some of the aforementioned publications, disallows using content-based methods.
+				\parvspace{}
 
@@
 
+		{
+			\color{gray}
+			\hspace{-1em}
+			\vrule{}
+			\hspace{+1em}
+		}
+
 		\begin{column}{0.45\textwidth}
@@
 				The DonorsChoose.org dataset is composed of past donations featuring $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects.
-The corpus provides significantly more transactions with more detailed item and transaction information compared to, e.g., the popular MovieLens dataset.
-An exemplary itemized view of the augmented dataset is shown in~\autoref{tab:IllustrativeTable} with the augmented data to the right of the separator.
+In contrast to, e.g., the popular MovieLense dataset, the DonorsChoose.org corpus provides significantly more transactions with more detailed item and transaction information as exemplary seen in~\autoref{tab:IllustrativeTable}.
+				\parvspace{}
 
-				\vspace*{-.5\baselineskip}  % TODO: Fix this HACK
+				The augmented data which is to the right of the separator in~\autoref{tab:IllustrativeTable} is composed of the metadata of SVD, KNN, TF-IDF and word-embedding using fastText~\cite{scikit-learn,rehurek_lrec,DBLP:journals/corr/BojanowskiGJM16}.
+Vector representations of items are the normalized sum of the vectors of the normalized embeddings of the individual words.
+In order to work with the data in an efficient way, $100,000$ transactions are sampled.
+				\parvspace{}
+
+				The recall in a Top-N test set is used as score of how good an algorithm is able to recommend an item.
+				\begin{enumerate}
+					\item For each user, first $100$ items with which the user has not interacted are selected.
+					\item The algorithm then ranks an item with which the user has interacted and the $100$ randomly sampled items.
+					\item The position of the item with which the user has interacted in the ranked test set may now be taken as the recall in a Top-N test set.
+				\end{enumerate}
+			\end{block}
+		\end{column}
+	\end{columns}
+
+	\begin{columns}[t]
+		\begin{column}{0.645\textwidth}
 			\begin{table}[ht]
@@
 				\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/table}}}
-					\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}\label{tab:IllustrativeTable}
+				\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}%
+				\label{tab:IllustrativeTable}
 			\end{table}
+		\end{column}
+	\end{columns}
 
-				SVD and KNN are used as representatives for collaborative filtering techniques and TF-IDF and word-embedding as content-based filters~\cite{scikit-learn,rehurek_lrec}.
-Hereby, the otherwise intrinsic inductive bias is reduced.
-The word-embedding relies on fastText and utilizes pre-trained vectors~\cite{DBLP:journals/corr/BojanowskiGJM16}.
-Vector representations of items are the normalized sum of the vectors of the normalized embeddings of the individual words.
-In order to work with the data in an efficient way, transactions are sampled.
-For this study a sample-size of $100,000$ was chosen.
-This represents a fair balance between required computing time and ability to generalize.
-
-				The recall in a Top-N test set is used as score of how good an algorithm is able to recommend an item.
-				\begin{enumerate*}[label= (\arabic*)]
-					\item For each user, first $100$ items with which the user has not interacted with are selected.
-					\item The algorithm is then requested to rank an item with which the user has interacted with but which was not used for building the user's profile and the $100$ randomly sampled items.
-It is assumed that the random $100$ items are of low interest to the user.
-					\item The position of the item with which the user has interacted with in the ranked test set may now be taken as the recall in a Top-N test set.
-				\end{enumerate*}
-			\end{block}
+	\begin{columns}[t]
+		\begin{column}{0.945\textwidth}
+			\color{gray}
+			\vspace{0.5em}
+			\hrule{}
+			\vspace{0.5em}
 		\end{column}
@@
 							}
-							\caption{The frequency of the number of interactions per user without outliers is shown in~\subref{fig:InteractionFrequency} and the distribution of the transformed interaction strength is shown in~\subref{fig:InteractionStrength}.}\label{fig:Interactions}
+							\caption{The frequency of the number of interactions per user without outliers is shown in~\subref{fig:InteractionFrequency} and the distribution of the transformed interaction strength is shown in~\subref{fig:InteractionStrength}.}%
+							\label{fig:Interactions}
 						\end{figure}
@@
 					\begin{column}{0.49\textwidth}
-						Statistical information about the performances of the individual machine learners in the learning subsystem are visualized in~\autoref{fig:MetaLearnerStatistics}.
+						Statistical features about the performances of the individual machine learners in the learning subsystem are visualized in~\autoref{fig:MetaLearnerStatistics}.
 Overall, content-based filters are significantly better in achieving a low recall-position.
@@
 							}
-							\caption{Statistical features of the distributions of the recall-positions of the learning subsystem are shown in~\subref{fig:MetaLearnerStatistics}.
-The dashed green lines indicate the mean, the straight orange lines the median.
+							\caption{Statistical features of the recall-positions of the learning subsystem are shown in~\subref{fig:MetaLearnerStatistics}.
+The dashed green lines indicate the means, the straight orange lines the medians.
 The percentage below each algorithm indicates how often it is the best possible algorithm.
 To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.
-							The performance of the meta-learner system addressing the ASP is shown in~\subref{fig:MetaLearnerPerformance}.
-The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}\label{fig:MetaLearner}
+							The performance of the meta-learner system is shown in~\subref{fig:MetaLearnerPerformance}. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}%
+							\label{fig:MetaLearner}
 						\end{figure}
@@
 			\end{block}
+		\end{column}
+	\end{columns}
+
+	\begin{columns}[t]
+		\begin{column}{0.945\textwidth}
+			\color{gray}
+			\vspace{0.5em}
+			\hrule{}
+			\vspace{0.5em}
 		\end{column}

### 2019-04-10 doc/paper/main.tex
paper/main.tex: Empty page style
Get rid of an annoying chapter hint in the header by switching to a
blank page style using `\pagestyle`. Comment out `\makeboth`
accordingly and add a note.
{paper,poster}/main.tex: Tweaks and suggestions

@@
 	\lstset{basicstyle=\ttfamily,breaklines=true}  % Prettier code highlighting style
-	\pagestyle{myheadings}  % Prettier page format with header but without footer
+	\pagestyle{empty}  % Prettier page format without header and footer
 
@@
 	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
-	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, collinsa@tcd.ie, aizawa@nii.ac.jp}
+	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, ancollin@tcd.ie, aizawa@nii.ac.jp}
 }
@@
 \maketitle  % Typeset the header of the contribution
-\markboth{}{}  % Clear the section and author from the page header
+%\markboth{}{}  % Clear the section and author from the page header; also see `\pagestyle`
 
@@
 Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning task.
-We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich and vast corpus is a suitable candidate.
+We are augmenting a publicly available dataset intrinsically about recommendations which to our best knowledge has not been used for meta-learning before in the scientific community.
+Yet due to its feature-rich and vast corpus is a suitable candidate.
 The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}).
@@
 Their dataset composed of past donations features $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects.
-The corpus provides significantly more transactions with more detailed item and transaction information compared to, e.g., the popular MovieLens dataset.
-An exemplary itemized view of the augmented dataset is shown in~\autoref{tab:IllustrativeTable}.
+This work uses the eighth version of the dataset hosted at \href{https://www.kaggle.com/donorschoose/io}{kaggle.com/donorschoose/io}.
+An exemplary itemized view of the augmented dataset is shown in~\autoref{tab:IllustrativeTable} with an outline of the plain data to the left of the separator.
 
@@
 
-In a first step, two collaborative filtering techniques and two content-based filtering techniques are applied.
+In a first step, we apply two collaborative filtering techniques and two content-based filtering techniques.
 The performance measures of the single algorithms are amended to the table.
-Next, aggregated user and item statistics are calculated and added to the table.
+Next, we calculate aggregated user and item statistics and added them to the table.
 Lastly, four exemplary meta-learners are applied and the performance measures of the individual approaches are added to the corpus.
@@
 Lastly, the donated amount is transformed to a transaction strength in the range of unity to five in analogy to a rating score.
-This step reduces the influence of outliers respectively uncommon donated amounts.
+This step reduces the influence of outliers.
 
@@
 \begin{enumerate*}[label= (\arabic*)]
-	\item For each user, first $100$ items with which the user has not interacted with are selected.
-	\item The algorithm is then requested to rank an item with which the user has interacted with but which was not used for building the user's profile and the $100$ randomly sampled items.
+	\item For each user, first $100$ items with which the user has not interacted are selected.
+	\item The algorithm is then requested to rank an item with which the user has interacted but which was not used for building the user's profile and the $100$ randomly sampled items.
 It is assumed that the random $100$ items are of low interest to the user.
-	\item The position of the item with which the user has interacted with in the ranked test set may now be taken as the recall in a Top-N test set.
+	\item The position of the item with which the user has interacted in the ranked test set may now be taken as the recall in a Top-N test set.
 \end{enumerate*}
@@
 
-\subsection{Statistics and Application of Learning Subsystem}
+\subsection{Statistics and Application of the Learning Subsystem}
 The meta-learning system processes the metadata of the learning subsystem and further statistics.
@@
 	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem.
-The dashed green lines indicate the mean, the straight orange lines the median.
+The dashed green lines indicate the means, the straight orange lines the medians.
 The percentage below each algorithm indicates how often it is the best possible algorithm.

### 2019-04-10 doc/poster/main.tex
{paper,poster}/main.tex: Tweaks and suggestions

@@
 	\inst{2}National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan
-	\and \href{mailto:beelj@tcd.ie}{beelj@tcd.ie}, \href{mailto:collinsa@tcd.ie}{collinsa@tcd.ie}, \href{mailto:aizawa@nii.ac.jp}{aizawa@nii.ac.jp}
+	\and \href{mailto:beelj@tcd.ie}{beelj@tcd.ie}, \href{mailto:ancollin@tcd.ie}{ancollin@tcd.ie}, \href{mailto:aizawa@nii.ac.jp}{aizawa@nii.ac.jp}
 }
@@
 
-				Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning task.
-We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich and vast corpus is suitable.
+				Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way.
+We are augmenting a public domain dataset intrinsically about recommendations which to our best knowledge has not been used for meta-learning before in the scientific community.
+Yet due to its feature-rich and vast corpus is suitable.
 			\end{block}
@@
 				The DonorsChoose.org dataset is composed of past donations featuring $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects.
-In contrast to, e.g., the popular MovieLense dataset, the DonorsChoose.org corpus provides significantly more transactions with more detailed item and transaction information as exemplary seen in~\autoref{tab:IllustrativeTable}.
+It provides more feature-richt transactions in contrast to, e.g., the popular MovieLens dataset as outlined in~\autoref{tab:IllustrativeTable}.
 				\parvspace{}

### 2019-04-12 doc/presentations/Research Proejct Presentation @ AMIR.tex
doc/presentations: Add presentation for AMIR 2019

\documentclass[aspectratio=169]{beamer}
\usepackage[utf8]{inputenc}  % Required for umlauts
\usepackage[english]{babel}  % Language
%\usepackage[sfdefault]{roboto}  % Enable sans serif font roboto
%\usepackage{libertine}  % Enable this on Windows to allow for microtype
\usepackage[T1]{fontenc}  % Required for output of umlauts in PDF

\usepackage{mathtools}  % Required for formulas

\usepackage{caption}  % Customize caption aesthetics
\usepackage{tcolorbox}  % Fancy colored boxes
\usepackage{color}
\usepackage{xcolor}  % Highlighting
\usepackage{soul}

\usepackage{booktabs}  % Using pandas' LaTeX output
\usepackage{multirow}  % Enable fancy table structure

\usepackage{listings}  % Insert programming code
\usepackage{graphicx}  % Required to insert images
\usepackage{subcaption}  % Enable sub-figure
\usepackage[space]{grffile}  % Insert images baring a filename which contains spaces
\usepackage{float}  % Allow to forcefully set the location of an object

\usepackage[tracking=true]{microtype} % Required to change character spacing

\usepackage[backend=biber,autocite=footnote,style=authortitle-comp,sorting=none,giveninits=true,doi=false,isbn=false,url=false,eprint=false]{biblatex}
\usepackage{csquotes}  % Ensure proper quotation of texts with babel and polyglossia with biblatex
\usepackage{hyperref}  % Insert clickable references

\usepackage{datetime}  % Flexible date specification

\usepackage{geometry}
\usepackage{scrextend}  % Allow arbitrary indentation

\usepackage{appendixnumberbeamer}  % Fancy page numbering excluding the appendix

% Compile notes into a separate file readable by pdfpc using a custom package which overwrite the `note` macro
\usepackage{../pdfpcnotes}

\addbibresource{../literature.bib}
\renewcommand{\footnotesize}{\tiny}
%\renewcommand*{\bibfont}{\scriptsize}

\newcommand{\leadingzero}[1]{\ifnum#1<10 0\the#1\else\the#1\fi}
\newcommand{\todayddmmyyyy}{\leadingzero{\day}.\leadingzero{\month}.\the\year}
\newcommand{\mathcolorbox}[2]{\colorbox{#1}{$\displaystyle #2$}}

\makeatletter
% Fix subfig in beamer style presentation
\let\@@magyar@captionfix\relax

% Insert [short title] for \section in ToC
\patchcmd{\beamer@section}{{#2}{\the\c@page}}{{#1}{\the\c@page}}{}{}
% Insert [short title] for \section in Navigation
\patchcmd{\beamer@section}{{\the\c@section}{\secname}}{{\the\c@section}{#1}}{}{}
% Insert [short title] for \subsection in ToC
\patchcmd{\beamer@subsection}{{#2}{\the\c@page}}{{#1}{\the\c@page}}{}{}
% Insert [short title] for \subsection in Navigation
\patchcmd{\beamer@subsection}{{\the\c@subsection}{#2}}{{\the\c@subsection}{#1}}{}{}
\makeatother

\setbeamercolor{title}{fg=orange}
\setbeamertemplate{title}{
	\color{orange}
	\textbf{\inserttitle}
}
\setbeamercolor{tableofcontents}{fg=orange}
\setbeamercolor{section in toc}{fg=black}
\setbeamercolor{subsection in toc}{fg=black}
\setbeamertemplate{frametitle}{
	\color{orange}
	\begin{center}
		\textbf{\insertframetitle} \\
		{\small \insertframesubtitle}
	\end{center}
}
\setbeamertemplate{footline}[text line]{
	\parbox{\linewidth}{
		\tiny
		\color{gray}
		AMIR 2019
		\hfill
		Gordian (\href{mailto:gordian.edenhofer@gmail.com}{gordian.edenhofer@gmail.com})
		\hfill
		\insertframenumber/\inserttotalframenumber%
	}
}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{itemize item}{\color{black}$\bullet$}
\setbeamertemplate{itemize subitem}{\color{black}$\circ$}
\setbeamercolor{block title}{fg=black}
\captionsetup{font=scriptsize,labelfont={bf,scriptsize}}

% Customize code blocks
\lstset{basicstyle=\ttfamily,breaklines=true,showstringspaces=false,commentstyle=\color{red},keywordstyle=\color{blue}}

\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
\subtitle{``Meta-Learning for Recommender Systems''}
\author[Edenhofer]{\href{mailto:gordian.edenhofer@gmail.com}{Gordian Edenhofer}}
\institute[NII]{
	Working Group of Prof.~Dr.~Beel, Trinity College Dublin \\
	Laboratory of Prof.~Dr.~Akiko~Aizawa, Nationa Institute of Informatics
}
\date[AMIR 2019]{AMIR, \formatdate{14}{04}{2019}}
\subject{Natural Language Processing and Machine Translation}

\begin{document}

\pagenumbering{arabic}

\begin{frame}[plain]  % NOTE: Adding "noframenumbering" as argument confuses `pdfpc`; see https://github.com/pdfpc/pdfpc/issues/367
	\titlepage%
\end{frame}

\section[Introduction]{Research Problem}
\frame{\vfill\centering\tableofcontents[sectionstyle=show/shaded,subsectionstyle=show/hide]\vfill}

% TODO: Some advise for the presentation at AMIR: It would be good if you could somehow address the scope of the workshop, i.e. don't argue "we need more detasets for meta learning", but argue "we need to explore more meta learning in the field of recommender systems, and in this field there are few suitable datasets. If you have time, you might also adjust this in the paper a bit.

\subsection{Lack of Datasets}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{itemize}
		\item Meta-learning for recommender systems
		\begin{itemize}
			\item Combine strengths of individual learners
			\item Incorporate more transaction details
		\end{itemize}
		\item Absence of recommendation datasets with metadata
		\begin{itemize}
			\item Time-consuming and cumbersome to construct and implement learning subsystem
			\item Drains resources from actual meta-learning experiment
			\item Manual augmentation is often redundant~\autocite{CUNHA2018128,DBLP:journals/corr/abs-1805-12118,Ekstrand:2012:RFP:2365952.2366002}
		\end{itemize}
	\end{itemize}

	\note{Cumbersome in the sense of, e.g., choice of metric}
	\note{Redundant augmentation as 5 out of 7 reviewed use MovieLense data}
\end{frame}

\subsection{Augmenting DonorsChoose.org}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{itemize}
		\item Augment dataset
		\begin{itemize}
			\item Find recommendation dataset suitable for meta-learning
			\item Ensure sufficient user-, item- and transaction-information
			\item Add metadata of single recommender algorithms, statistics, etc.~to the dataset
		\end{itemize}
		\item Encourage evaluation of meta-learner experiments on this dataset
	\end{itemize}

	\note{Allow others to skip augmentation of proper dataset}
\end{frame}

\section[Methodology]{Augmentation}
\frame{\vfill\centering\tableofcontents[sectionstyle=show/shaded,subsectionstyle=show/hide]\vfill}

\subsection{The DonorsChoose.org Dataset}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{itemize}
		\item DonorsChoose.org transaction dataset
		\begin{itemize}
			\item \$686M raised
			\item 4,69M transactions (donations); 2,12M users (donors); 1,11M items (projects)
		\end{itemize}
		\item Available features
		\begin{itemize}
			\item User: location, teacher status
			\item Item: location, category, descriptions, funding goals, creator
			\item Transaction: strength (donated amount), time
		\end{itemize}
		\item Augmentation
		\begin{itemize}
			\item Learning subsystem: two collaborative \& two content-based recommender algorithms
			\item Statistics: aggregated user and item statistics
			\item Exemplary meta-learners: algorithm selection problem via stacking hybrid ensemble
		\end{itemize}
	\end{itemize}

	\note{metadata-rich dataset is important for good recommendation}
	\note{DonorsChoose.org corpus a perfect fit due to instrinsic topic-match}
\end{frame}

\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{figure}
		\centering
		\includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio]{{{../res/Illustrative example of the overall design of the augmented transaction table}}}
		\caption{Illustrative example of the overall design of the augmented transaction table with
		amended learning subsystem performance scores, statistics and meta-learner information.}
	\end{figure}

	\note{plain data to the left; augmented to the right}
\end{frame}

\subsection{Dataset Preparation}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{itemize}
		\item House keeping
		\begin{itemize}
			\item Merging duplicate transaction
			\item Remove stop-words
			\item Drop transactions with NaN as location
		\end{itemize}
		\item Requiring users to have donated at least twice (training and testing)
		\item Transformation
		\begin{itemize}
			\item DonationAmount to interaction strength
			\item Sampling 100,000 transaction
		\end{itemize}
	\end{itemize}

	\note{preparation overall preserves a little more than half of the data}
	\note{requiring users to donate twice reduces number of transactions but is necessary}
	\note{conversion to interaction strength incorporates outliers}
\end{frame}

\subsection{Learning Subsystem}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{itemize}
		\item Cross-validation using $5$ folds
		\item Top-N accuracy using the recall~\autocite{Cremonesi:2010:PRA:1864708.1864721}
		\begin{itemize}
			\item Randomized subset of $100$ projects the user has not donated to
			\item One project to which the user has donated to
			\item Recall@N is predicted position of donated project in the subset of $101$ projects
		\end{itemize}
	\end{itemize}

	\begin{table}
		\scriptsize
		\centering
		\begin{tabular}{l|lll}
			Filtering method & Algorithm & Computational method & Yields \\
			\hline
			\hline
			collaborative & KNN & nearest-neighbor (2-norm) & RMSE, MAE, \colorbox{yellow}{Recall@N} \\
			& SVD & matrix factorization & RMSE, MAE, \colorbox{yellow}{Recall@N} \\
			\hline
			content-based & TF-IDF & term frequency & cosine similarity, \colorbox{yellow}{Recall@N} \\
			\hline
			content-based, neural network & fastText & word-embedding & cosine similarity, \colorbox{yellow}{Recall@N} \\
		\end{tabular}
		\caption{Architecture of the learning subsystem with a list of properties for each algorithm.}
	\end{table}

	\note{top-n instead of a metric ensures comparability of results}
\end{frame}

\subsection{Statistics and Application of Learning Subsystem}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{itemize}
		\item Holdout-validation using $80\%$ train-test-split
		\item Statistics
		\begin{itemize}
			\item Aggregated user information on value counts for past donations
			\item Aggregated item location, category, etc.~information grouped by user
		\end{itemize}
		\item Meta-learner approaches
		\begin{itemize}
			\item Transaction classification via a decision tree
			\item Error prediction using gradient boosting
			\item User-clustering using K-Means
			\item Stacking decision tree as classifier
		\end{itemize}
	\end{itemize}

	\note{easy to compute user-statistics based on train set}
	\note{valueable features for meta-learner}
\end{frame}

\section[Results]{Augmented Corpus}
\frame{\vfill\centering\tableofcontents[sectionstyle=show/shaded,subsectionstyle=show/hide]\vfill}

\subsection{Shape}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{itemize}
		\item More than half of transactions preserved ($>>$ sample size)
		\item Sample of 100,000 transactions: 21,087 unique users and 91,827 unique projects
	\end{itemize}

	\begin{figure}[ht]
		\centering
		\subcaptionbox{Transactions per user\label{fig:dist_number_of_interactions_per_user}}{
		\includegraphics[width=0.35\textwidth,height=\textheight,keepaspectratio]{{{../res/DonorID - Distribution of number of interactions per user}}}
		}
		\hspace{2em}
		\subcaptionbox{Ratings\label{fig:dist_transaformed_ratings}}{
		\includegraphics[width=0.35\textwidth,height=\textheight,keepaspectratio]{{{../res/DonationAmount - Distribution of ratings for logarithmic bins and excluded outliers}}}
		}
		\caption{Distribution of the number of transactions per user and the rating scores to which the donated amount has been transformed to.}
		\label{fig:dataset_sample_dist}
	\end{figure}
\end{frame}

\subsection{Learning Subsystem}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{figure}
		\centering
		\includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio]{{{../res/Learning subsystem - Position in Top-N test set}}}
		\caption{Statistical features of the distribution of the donated item position in the Recall@N test set. The dashed green lines indicate the means, the straight orange lines the medians.}
	\end{figure}

	\note{most essential result of this work!}
\end{frame}

\subsection{Exemplary Meta-Learning Experiment}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{figure}
		\centering
		\includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
		\caption{Performance of the four meta-learners in comparison to the overall best algorithm.}
	\end{figure}

	\note{just a small experiment}
\end{frame}

\section{Conclusion}
\frame{\vfill\centering\tableofcontents[sectionstyle=show/shaded,subsectionstyle=show/hide]\vfill}

\subsection{Extensively Augmented DonorsChoose.org Dataset}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{itemize}
		\item Feature-rich and big corpus suitable for recommendations
		\item Extensively augmented features
		\begin{itemize}
			\item Learning subsystem
			\item Aggregated user and transaction statistics
			\item First success in solving the Algorithm Selection Problem via switching hybrid ensemble
		\end{itemize}
		{
		\setbeamertemplate{itemize item}{\color{black}$\Rightarrow$}
		\item Excellent candidate for further meta-learning experiments
		}
	\end{itemize}
\end{frame}

\section*{Thank You}
{
	\setbeamertemplate{footline}[text line]{}
	\begin{frame}
		\frametitle{\insertsection}
		\framesubtitle{\insertsubsection}

		\begin{columns}[t]
			\begin{column}{0.175\textwidth}
				\centering
				\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{{{../res/Profile picture of Gordian}}} \\
				Gordian
			\end{column}

			\begin{column}{0.175\textwidth}
				\centering
				\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{{{../res/Profile picture of Andrew}}} \\
				Andrew
			\end{column}

			\begin{column}{0.175\textwidth}
				\centering
				\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{{{../res/Profile picture of Akiko}}} \\
				Aizawa
			\end{column}

			\begin{column}{0.175\textwidth}
				\centering
				\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{{{../res/Profile picture of Joeran}}} \\
				Beel
			\end{column}
		\end{columns}

		\centering
		\vspace{3em}
		{\Large\inserttitle{}}
		\vspace{1em}
		\bfseries{\href{https://github.com/BeelGroup/Augmented-DonorsChoose.org-Dataset}{GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset}}
		\vspace{1em}
		\href{mailto:gordian.edenhofer@gmail.com}{gordian.edenhofer@gmail.com}
	\end{frame}
}

\appendix
\section*{Appendix}

\subsection{Meta-Learner}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\scalebox{.47}{
	\centering
	% Extract the table via the following command and add the necessary midrule to separate inputs from targets
	% meta_items.loc[train_idx][sorted(feature_columns) + ['SubalgorithmCategory'] + sorted(alg_acc_to_alg_columns.keys())].head(5).transpose().to_latex('meta_items: table head.tex', multirow=True, header=False)
	\input{"../res/meta_items: table head"}
	}
\end{frame}

\subsection{Meta-Learner}
\begin{frame}
	\frametitle{\insertsection}
	\framesubtitle{\insertsubsection}

	\begin{figure}
		\centering
		\subcaptionbox{Error prediction}{
		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/Meta-Learner Architecture: Error prediction algorithm}}}
		}
		\subcaptionbox{Classification}{
		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/Meta-Learner Architecture: Classification algorithm}}}
		}
		\caption{Meta-learner architecture for an error prediction- and a classification-approach.}
	\end{figure}
\end{frame}

\end{document}

### 2019-05-06 doc/paper/main.tex
paper/main.tex: Add LMU as affiliation and strip

@@
 \title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
-	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}}
-\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
+	}
+\author{Gordian~Edenhofer\inst{1,3} \and Andrew~Collins\inst{2} \and Akiko~Aizawa\inst{3} \and Joeran~Beel\inst{2,3}\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}}
 \authorrunning{G. Edenhofer et al.}  % Abbreviated author field
 \institute{
+	Ludwig Maximilian University of Munich, Faculty of Physics, Germany\\ \and
 	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
-	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, ancollin@tcd.ie, aizawa@nii.ac.jp}
+	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{g.edenhofer@campus.lmu.de, ancollin@tcd.ie, aizawa@nii.ac.jp, beelj@tcd.ie}
 }
@@
 The goal is to improve existing approaches by combining the strengths of several single machine learning systems~\cite{AIR:MetalearningSurveyOfTrendsAndTechnologiesLemke2015}.
-In recommender systems it is an emerging field of interest as meta-learning promises to utilize patterns in metadata as to retrieve the best possible match of item and user.
-In order to investigate meta-learning algorithms, the required metadata needs to be computed in advance.
+In recommender systems it is an emerging field of interest as it utilizes patterns in metadata.
+In order to investigate meta-learning, the required metadata needs to be computed in advance.
 

### 2019-05-06 doc/poster/main.tex
poster/main.tex: Drop an unimportant reference
{paper,poster}/main.tex: Fix spelling and grammar

@@
 
-				Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way.
+				Our objective is to address the data augmentation part in a comprehensive and reproducible way.
 We are augmenting a public domain dataset intrinsically about recommendations which to our best knowledge has not been used for meta-learning before in the scientific community.
-Yet due to its feature-rich and vast corpus is suitable.
+Yet due to its feature-rich and vast corpus it is suitable.
 			\end{block}
@@
 							\hspace{.5em}
-							\subcaptionbox{Perfromance\label{fig:MetaLearnerPerformance}}{
+							\subcaptionbox{Performance\label{fig:MetaLearnerPerformance}}{
 								\includegraphics[width=.45\textwidth,height=\textheight,keepaspectratio]{{{../res/meta_learner_performance_average_position}}}
